Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-24 analysis/paper/asymsam.Rmd
Cambia el sitio web de los datos.

All data used in this paper is freely available from their respective sources.
ERA5 data can be obtained via the Copernicus Climate Data Store ([\<https://cds.climate.copernicus.eu/cdsapp\#!/dataset/reanalysis-era5-pressure-levels-monthly-means\>](https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means){.uri}).
CMAP Precipitation data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at <https://psl.noaa.gov/data/gridded/data.cmap.html>.
The Oceanic Niño Index is available via NOAA's Climate Prediction Center: <https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt>.
The SAM, A\nobreakdash-SAM and S\nobreakdash-SAM indices are available at the public repository associated with this paper, at <https://github.com/eliocamp/asymsam/tree/master/analysis/data/derived_data>.

>>>>

All data used in this paper is freely available from their respective sources.
ERA5 data can be obtained via the Copernicus Climate Data Store ([\<https://cds.climate.copernicus.eu/cdsapp\#!/dataset/reanalysis-era5-pressure-levels-monthly-means\>](https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means){.uri}).
CMAP Precipitation data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at <https://psl.noaa.gov/data/gridded/data.cmap.html>.
The Oceanic Niño Index is available via NOAA's Climate Prediction Center: <https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt>.
The SAM, A\nobreakdash-SAM and S\nobreakdash-SAM indices are available at <http://www.cima.fcen.uba.ar/~elio.campitelli/asymsam/>.
